---
title: "HW10_315"
author: "Justin Song - jjs5874 - Scott - https://github.com/jujiwoo/HW10_315"
date: "2024-04-21"
output:
  pdf_document: default
  html_document: default
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=5, fig.width=10, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=100))
```

```{r, echo=FALSE, results='hide', message=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)
library(mosaic)
library(MatchIt)
library(moderndive)
library(effectsize)

redline = read.csv('redlining.csv')
grocery = read.csv('groceries.csv')
```

# Problem 1

**1) Question: Is there an association between the number of FAIR policies and the racial/ethic composition of a ZIP code**

**2) Approach: What approach/statistical tool did you use to answer the question?**
To answer the question, I used a linear regression model. Specifically, I fitted a linear regression with the number of FAIR policies per 100 housing units as the dependent variable, and the minority percentage, fires per 100 housing units, percent of housing units built before WWII, and median family income as the independent variables.


**3) Results: What evidence/results did your approach provide to answer the question? (E.g. any numbers, tables, figures as appropriate.)**
```{r, echo=FALSE}
lm = lm(policies ~ minority + fire + age + income, data = redline)
get_regression_table(lm, conf.level = 0.95, digits=3)
standardize_parameters(lm)
```

**4) Conclusion:**
Minority: A 1 percentage point increase in the minority population is associated with a 0.008 increase in the number of FAIR policies per 100 housing units (95% CI: 0.003 to 0.014), suggesting potential redlining.   

The results suggest evidence of an association between higher minority population percentages in ZIP codes and increased reliance on FAIR home insurance policies, which could indicate potential redlining practices in the private insurance market after adjusting for other factors.

\newpage

# Problem 2

**Part A. What kind of price differences do we see across the different stores**

```{r, echo=FALSE}
avg_price_by_store =  grocery %>%
  group_by(Store) %>%
  summarise(avg_price = mean(Price, na.rm = TRUE)) %>%
  arrange(desc(avg_price))

ggplot(avg_price_by_store, aes(y = avg_price, x = reorder(Store, avg_price))) +
  geom_col() +
  labs(x = "Store", y = "Average Price", 
       title = "Average Price of Products by Store",
       caption = "The bar chart displays the average price of products sold at different grocery stores."
) +
  coord_flip()
```

**Part B.**

```{r, echo=FALSE}

store_counts = grocery %>%
  group_by(Product) %>%
  summarise(num_stores = n_distinct(Store))

ggplot(store_counts, aes(y = Product, x = num_stores)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Stores Selling Each Product",
       x = "Number of Stores",
       y = "Product", caption = "The bar chart illustrates the number of distinct grocery stores that sell each product listed on the y-axis.")
```

**Part C.**

```{r, echo=FALSE}

model = lm(Price ~ Type + Product, data = grocery)
get_regression_table(model)

```

Compared with ordinary grocery stores (like Albertsons, HEB, or Krogers), convenience stores charge somewhere between $0.92 and $0.41 dollars less for the same product.


**Part D.**

```{r, echo=FALSE}
model = lm(Price ~ Store + Product, data = grocery)
get_regression_table(model)
```
Kroger Fresh Fare, with a coefficient of -0.902, tends to charge lower prices along with Walmart, with a coefficient of -0.993.

The two stores with the highest prices when comparing the same product are Wheatsville Food Co-Op: with a coefficient of 0.290 and Whole Foods with a coefficient of  0.364.


**Part E.**

The coefficient for HEB in the regression model (-0.646) suggests that it charges slightly lower prices compared to Central Market(-0.573), but the difference is not significantly large. This difference falls within the range of variations observed among other stores, indicating that Central Market likely charges a similar amount to HEB for the same product rather than significantly more or less. 

The difference between the coefficients for H-E-B and Central Market (0.07257) is smaller than the largest difference observed between Walmart and Kroger (0.28923). This suggests that the difference in pricing strategies between H-E-B and Central Market is relatively modest compared to the variations observed among other stores such as Walmart and Kroger.


**Part F**

```{r, echo=FALSE}
grocery = grocery %>% 
  mutate(Income10K = Income / 10000)


model_income = lm(Price ~ Income10K + Product, data = grocery)

get_regression_table(model_income)
```
Based on the coefficient (-0.014090) for Income10K, consumers in poorer ZIP codes tend to pay less for the same product on average, because a negative coefficeint indicates suggests that as Income10K increases (indicating higher income), the price tends to decrease. 

A one-standard deviation increase in the income of a ZIP code seems to be associated with a 0.014 standard-deviation change in the price that consumers in that ZIP code expect to pay for the same product.